### 2016-11-17 ResearchStatement/main.tex
Minor tweaks

Unlike traditional product applications, using ML for social action
requires that we know the model is making decisions for the right reasons.
Much of my work in optimization has been in understanding how complex systems work~\cite{goldman:2015:cgpanalysis,goldman:2016:p3hiff},
and ML will require such analysis as currently much of its effectiveness is poorly understood.
Social action ML will also require learning
from comparatively small training sets, which will likely result in new advancements
in how to repurpose existing models from other tasks. However, if we can rise to the challenge
I believe ML can help those who need it most.

>>>>

Unlike traditional product applications, using ML for social action
requires that we know the model is making decisions for the right reasons.
Much of my work in optimization has been in understanding how complex systems work~\cite{goldman:2015:cgpanalysis,goldman:2016:p3hiff},
and ML will require such analysis to better understand its effectiveness.
Social action ML will also require learning
from comparatively small training sets, which will likely result in new advancements
in how to repurpose existing models from other tasks. However, if we can rise to the challenge
I believe ML can help those who need it most.

### 2016-11-17 TeachingStatement/main.tex
Minor tweaks

\section{Teaching Medium-Sized Classes}
Due to my previous success as a Lab Instructor, I was offered a
position as Lead Instructor for the second level undergraduate
programming course. This class is designed to introduce the students,
who learn Python in the first semester, to C++11. They learn
everything from basic syntax and STL tools to templates and how
to building their own data structures with dynamic memory.
I was given full autonomy to create course content, including
lectures, assignments, and assessments. To help with grading
assignments and lab work created by the 37 students, the
department assignment me two Lab Instructors.
I am proud to report that I received an average
of 3.81 out of 4 in post course student assessment.

@@

\section{Future Goals}
While much of my teaching experience has been with introductory
programming courses, I am also interested in teaching higher level
and theory based courses. Artificial intelligence and machine learning
are common courses which coincide strongly with my research interests.
Algorithms, discrete math, and graph theory are topics that I believe
present exciting challenges for keeping students engaged.
From previous work I have also acquired significant knowledge of
introductory and high performance C++ and would enjoy teaching classes
on those topics.

>>>>

\section{Teaching Medium-Sized Classes}
Due to my previous success as a Lab Instructor, I was offered a
position as Lead Instructor for the second level undergraduate
programming course. This class is designed to introduce the students,
who learn Python in the first semester, to C++11. They learn
everything from basic syntax and STL tools to templates and how
to build their own data structures with dynamic memory.
I was given full autonomy to create course content, including
lectures, assignments, and assessments. To help with grading
assignments and lab work created by the 37 students, the
department assignment me two Lab Instructors.
I am proud to report that I received an average
of 3.81 out of 4 in post course student assessment.

@@

\section{Future Goals}
While much of my teaching experience has been with introductory
programming courses, I am also interested in teaching higher level
and theory based courses. Artificial intelligence and machine learning
are common courses which coincide strongly with my research interests.
Algorithms, discrete math, and graph theory are topics that I believe
present exciting challenges for keeping students engaged.
From previous work I have also acquired significant knowledge of
introductory and high performance C++ and would enjoy teaching classes
on those topics. The time I have spent working for Google has also given
me new insight into the topics students will need in order to succeed
in industry.
